COMPAS Race Analysis

### 2022-03-28 race compas analysis.Rmd

```{python}
# meta = MetaFairClassifier(tau=0.8, sensitive_attr='race', type='fdr', seed=1234567)
# 
# meta.fit(train_BLD)
# y_pred_META = meta.predict(test_BLD)
# y_pred_META = y_pred_META.labels.flatten()
```

```{python}
# acc_AD = accuracy_score(y_test, y_pred_META)
# print(f'[ Meta-Classification] The test accuracy of the algorithm is: {acc_AD: .2%}')
```

>>>>

```{python}
meta = MetaFairClassifier(tau=0.8, sensitive_attr='race', type='fdr', seed=1234567)

meta.fit(train_BLD)
y_pred_META = meta.predict(test_BLD)
y_pred_META = y_pred_META.labels.flatten()
```

```{python}
acc_AD = accuracy_score(y_test, y_pred_META)
print(f'[ Meta-Classification] The test accuracy of the algorithm is: {acc_AD: .2%}')
```
